### 2009-02-23 doc/ws-programming-tutorial/doc/tex_tls_echoservice/tls_echoservice.tex
I wrote more in for the time service and try to push the other services further

@@

\begin{program}
\lstsetCPP
\lstinputlisting
	[
	label=lst:arcecho_arched_xml,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/clients/tlsechoclient/tlsechoclient.cpp}
\end{program}

\begin{program}
\lstsetCPP
\lstinputlisting
	[
	label=lst:arcecho_arched_xml,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/tlsechoservice/tlsechoservice.cpp}
\end{program}

\lstsetARCHEDXML
\begin{program}
\lstinputlisting
	[
	label=lst:arcecho_arched_xml,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/tlsechoservice/arched_tls_echoservice.xml}
\end{program}

\lstsetKSH
\begin{program}
\begin{lstlisting}[
label=lst:invokation_arched_timeservice,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ rm -f /var/log/arched.log
$ arched -c arched_echoservice.xml  && echo jo ||echo n
$ tail -n100 -f /var/log/arched.log
$ killall arched
\end{lstlisting}
\end{program}

\lstsetKSH
\begin{program}
\begin{lstlisting}[
label=lst:invokation_arched_timeservice,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ ./echoclient
Tue Feb 17 17:04:08 2009
\end{lstlisting}
\end{program}

\lstsetJUSTXML
\begin{program}
\begin{lstlisting}[
label=lst:timeservice_cpp_source,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:echo="urn:echo" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
	<soap-env:Body>
		<echoRequest:echo>
			<echo:say>Der_Berg_ruft</echo:say>
		</echoRequest:echo>
	</soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
\end{program}

\lstsetJUSTXML
\begin{program}
\begin{lstlisting}[
label=lst:timeservice_cpp_source,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:echo="urn:echo" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <echo:echoResponse>
      <echo:hear>[ Der_Berg_ruft ]</echo:hear>
    </echo:echoResponse>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
\end{program}

>>>>

4 types:
                <KeyPath>./clientKey.pem</KeyPath>
                <CertificatePath>./clientCert.pem</CertificatePath>
                <CACertificatePath>./serviceCA.pem</CACertificatePath>

@@

\lstsetCPP
\lstinputlisting
	[
	label=lst:arcecho_arched_xml,float,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/clients/tlsechoclient/tlsechoclient.cpp}

\lstsetCPP
\lstinputlisting
	[
	label=lst:arcecho_arched_xml,float,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/tlsechoservice/tlsechoservice.cpp}

\lstsetARCHEDXML
\lstinputlisting
	[
	label=lst:arcecho_arched_xml,float,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/tlsechoservice/arched_tls_echoservice.xml}

\lstsetKSH
\begin{lstlisting}[
label=lst:invokation_arched_timeservice,float,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ rm -f /var/log/arched.log
$ arched -c arched_echoservice.xml  && echo jo ||echo n
$ tail -n100 -f /var/log/arched.log
$ killall arched
\end{lstlisting}

\lstsetKSH
\begin{lstlisting}[
label=lst:invokation_arched_timeservice,float,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ ./echoclient
Tue Feb 17 17:04:08 2009
\end{lstlisting}

\lstsetJUSTXML
\begin{lstlisting}[
label=lst:timeservice_cpp_source,float,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:echo="urn:echo" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
	<soap-env:Body>
		<echoRequest:echo>
			<echo:say>Der_Berg_ruft</echo:say>
		</echoRequest:echo>
	</soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}

\lstsetJUSTXML
\begin{lstlisting}[
label=lst:timeservice_cpp_source,float,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:echo="urn:echo" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <echo:echoResponse>
      <echo:hear>[ Der_Berg_ruft ]</echo:hear>
    </echo:echoResponse>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
